---
title: "Production forecast error calculations for Finnish data"
output: html_document
---

Code is based on Esa Turkulainen's https://github.com/FRCBS/forecast-demo/blob/master/forecast_script_wo_weekly.Rmd 
and Merel Wemelsfelder https://github.com/MerelWemelsfelder/blood_demand_forecast_NL/blob/master/forecast_script.Rmd .


```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
# echo "rmarkdown::render('forecast_script_FIN_wold.Rmd', clean=TRUE,output_format='html_document',output_file='results/forecast_script_FIN_wold_20201026.html')" | R --slave

# Set working directory
ROOTDIR <- "~/Work/proj/OPERATIONAL/blood_demand_forecast_NL/" # Your directory
DATADIR <- paste0("~/Work/proj/OPERATIONAL/production_forecasts/data/FACS_with202006and2020067_noBloodGroup")
HISTORYDIR <- paste0(ROOTDIR, "histories/") # monthly
MONTHLYDIR <- paste0(ROOTDIR, "histories/monthly_") # monthly
WEEKLYDIR <- paste0(ROOTDIR, "histories/weekly_") # weekly

knitr::opts_chunk$set(root.dir = ROOTDIR, warning = FALSE, message = FALSE) # No warnings for final output
knitr::opts_knit$set(root.dir = ROOTDIR, warning = FALSE, message = FALSE)

# Colorblind palette
# black, orange, sky blue, green,
# yellow, blue, vermilion, purple
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", 
                "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

# These colors work server side for now:
palette <- list(1, 1, 1, 0.7, "royalblue2", "deepskyblue1", "darkred", "darkgreen")
names(palette) <- c("alpha80", "alpha95", "alphaSeg", "alphaPred", "fill80", "fill95", "colPred", "colData")
```

```{r imports, message=FALSE, warning=FALSE, echo=FALSE}
library(forecast)
library(ggplot2)
library(gridExtra)
library(knitr)
library(plyr)
library(lubridate)
library(numbers)
library(data.table)
library(R.utils)
library(DT)
library(stringr)
library(hash)
library(zoo)
source("pffunctions.R")
# Set rolling window size in years
rw_years <- 3
start_date <- as.Date("2014-01-01")
```


```{r read_files, include = FALSE}
# Get all the files
files <- list.files(path = DATADIR, pattern = "FAC0091_*")  # Character vector of file names

# Compile a dataframe by going over all files
dlist <- list()
for (i in files) {
  # Read a single file to a df called d
  d <- read.delim(file = paste0(DATADIR, "/", i), header = FALSE, sep = ";", stringsAsFactors = FALSE, colClasses = 'character')
  
  if(length(d) == 26){
    d <- d[, !(names(d) %in% c("V10"))]  # The column numbers unfortunately vary between files, so we'll adjust
    }
  
  colnames(d) <- c("V1", "V2", "V3", "V4", "V5", "V6", "V7", "V8", "V9", "V10",
                   "V11", "V12", "V13", "V14", "V15", "V16", "V17", "V18", "V19", "V20",
                   "V21", "V22", "V23", "V24", "V25")  # This is done so as to have easier column handling later on
  dlist[[i]] <- d
}

d <- as.data.frame(rbindlist(dlist, fill = TRUE))
```

```{r modify_dataframe, include = FALSE}
# Divide into distributions (P) and returns (R)
P <- d[d$V1 == "P", ]
R <- d[d$V1 == "R", ]

# For distributions, we'll keep Distribution date, Quantity, ABO type, Volume, Exp date
keep <- c("V12", "V14", "V18", "V20", "V22", "V24")
distr <- P[keep]
colnames(distr) <- c("date", "product", "quantity", "ABO", "volume", "exp")

# For returns we keep the return date and quantity
keep <- c("V4", "V5", "V7")
retrn <- R[keep]
colnames(retrn) <- c("date", "product", "quantity")

# Datify
distr$date <- dmy(distr$date); distr$exp <- dmy(distr$exp)
retrn$date <- dmy(retrn$date)

# Numerify
distr$quantity <- as.numeric(distr$quantity); distr$volume <- as.numeric(distr$volume)
retrn$quantity <- as.numeric(retrn$quantity)

# Product codes for red cell products
red.codes <- c("budTR001", "A0071V00", "A0074V00", "A0092VA0", "A0092VB0", 
               "E3844V00", "E3845V00", "E3846VA0", "E3846VB0", "E3846VC0",
               "E3846V00", "E3847VA0", "E3847VB0", "E3847VC0", "E3847V00",
               "E3936VA0", "E3936VB0", "E3939V00", "E3940V00", "E4683V00",
               "E7668V00", "E7673V00", "E4999V00", "E5000V00")

red.distr <- distr[distr$product %in% red.codes, ]
red.retrn <- retrn[retrn$product %in% red.codes, ]

# Product codes for platelets
plat.codes <- c("budTR002", "trEnnApu", "A0004V00", "A0005V00", "A0006V00", "A0007V00", "A0008V00",
                "A0086VA0", "A0086VB0", "A0086V00", "A0088V00", "A0088VA0", "A0088VB0", "A0089V00",
                "A0089VB0", "A0089VA0", "A0090V00", "A0090VA0", "A0090VB0", "A0018V00", "A0020V00", 
                "A0021V00", "A0021VA0", "A0021VB0", "A0047V00", "A0049V00", "A0051V00", "A0054V00",
                "A0055V00", "A0056V00", "A0057V00", "A0059V00", "A0060V00", "A0067VA0", "A0067VB0",
                "A0067V00", "A0068VA0", "A0068VB0", "A0068V00", "A0075V00", "A0101V00", "A0102V00",
                "E3949V00", "E3953V00", "E3954V00", "E3955V00", "E3956V00", "E3957V00", "E3958V00",
                "E3959V00", "E3960V00", "E3961V00", "E3962V00", "E3963V00", "E3964V00", "E3965V00", 
                "E3966V00", "E3968VA0", "E3968VB0", "E3968V00", "E3970V00", "E3971V00", "E3973V00",
                "E3974V00", "E3976V00", "E3981V00", "E3995V00", "E3996V00", "E3997V00", "E3997VA0",
                "E3997VB0", "E4002V00", "E4004V00", "E6782V00", "E6783V00", "E6953V00", "E6860V00",
                "E6874VA0", "E6874V00", "E6874VB0", "E6875VB0", "E6875V00", "E7530V00", "E7530VA0",
                "E7530VB0", "E7531V00", "E7531VA0", "E7531VB0", "E6875VA0")

plat.distr <- distr[distr$product %in% plat.codes, ]
plat.retrn <- retrn[retrn$product %in% plat.codes, ]
```

#Get monthly values summarised by Laura
```{r}
monthly2004<- read.delim("~/Work/proj/OPERATIONAL/production_forecasts/data/kuukausimyynti.txt")
monthly2004$year<- as.factor(substr(monthly2004$kuukausi,1,4))
m2004<- as.factor(substr(monthly2004$kuukausi,6,9))
levels(m2004) <- c(8,7,2,4,12,6,10,3,11,9,1,5)
monthly2004$month <- as.character(m2004)
head(monthly2004,15)
```



```{r create_datasets, include = FALSE}
# Create a full sequence of dates for imputation purposes
all.dates <- (seq.Date(min(red.distr$date),
                       max(red.distr$date),
                       "day"))
###           ###
#   RED CELLS   #
###           ###
all.red <- aggregate(red.distr$quantity, by = list(red.distr$date), sum); colnames(all.red) <- c("date", "pcs")
# Merge into a whole set with NAs
all.red <- merge(x = data.frame(date = all.dates),
                 y = all.red,
                 all.x = TRUE)
# Replace with zeroes
all.red[is.na(all.red)] <- 0
# Cut to time after 2014
all.red <- all.red[all.red$date >= start_date, ]

###           ###
#  RED RETURNS  #
###           ###

all.red.retrn <- aggregate(red.retrn$quantity, by = list(red.retrn$date), sum); colnames(all.red.retrn) <- c("date", "pcs")
# Merge into a whole set with NAs
all.red.retrn <- merge(x = data.frame(date = all.dates),
                 y = all.red.retrn,
                 all.x = TRUE)
# Replace with zeroes
all.red.retrn[is.na(all.red.retrn)] <- 0
# Cut to time after 2014
all.red.retrn <- all.red.retrn[all.red.retrn$date >= start_date, ]




###           ###
#   PLATELETS   #
###           ###
all.plat <- aggregate(plat.distr$quantity, by = list(plat.distr$date), sum); colnames(all.plat) <- c("date", "pcs")
# Merge into a whole set with NAs
all.plat <- merge(x = data.frame(date = all.dates),
                  y = all.plat,
                  all.x = TRUE)
# Replace with zeroes
all.plat[is.na(all.plat)] <- 0
# Cut to time after 2014
all.plat <- all.plat[all.plat$date >= start_date, ]

###           ###
# PLAT RETURNS  #
###           ###
all.plat.retrn <- aggregate(plat.retrn$quantity, by = list(plat.retrn$date), sum); colnames(all.plat.retrn) <- c("date", "pcs")
# Merge into a whole set with NAs
all.plat.retrn <- merge(x = data.frame(date = all.dates),
                  y = all.plat.retrn,
                  all.x = TRUE)
# Replace with zeroes
all.plat.retrn[is.na(all.plat.retrn)] <- 0
# Cut to time after 2014
all.plat.retrn <- all.plat.retrn[all.plat.retrn$date >= start_date, ]
```



```{r datasets_monthly, include = FALSE, warning = FALSE}
# Aggregate all by months
red.monthly <- aggregate(pcs ~ month(date) + year(date), data = all.red, FUN = sum)
red.retrn.monthly <- aggregate(pcs ~ month(date) + year(date), data = all.red.retrn, FUN = sum)


plat.monthly <- aggregate(pcs ~ month(date) + year(date), data = all.plat, FUN = sum)
plat.retrn.monthly <- aggregate(pcs ~ month(date) + year(date), data = all.plat.retrn, FUN = sum)


```


```{r}
#Reduce returns from returns from deliveries to make numbers actual sales
red.monthly$pcs <- red.monthly$pcs - red.retrn.monthly$pcs
plat.monthly$pcs <- plat.monthly$pcs - plat.retrn.monthly$pcs
```


```{r}
head(red.monthly)
```

# Format month level data

```{r}
red.2004 <- monthly2004[,c("month","year","Punasoluvalmisteet")]
colnames(red.2004) <- colnames(red.monthly)
red.2004$`month(date)` <- as.integer(red.2004$`month(date)`)
red.2004$`year(date)` <- as.integer(as.character(red.2004$`year(date)`))
red.2004<- red.2004[order(red.2004$`year(date)`,red.2004$`month(date)`),]
red.2004$Date<- as.Date(as.yearmon(paste0(red.2004$`year(date)`,'-',red.2004$`month(date)`)))
head(red.2004)
```

# Check month level data

```{r}
red.monthly$Date<- as.Date(as.yearmon(paste0(red.monthly$`year(date)`,'-',red.monthly$`month(date)`)))
p <- ggplot(red.2004)
p <- p +  geom_line(aes(x=Date,y=pcs))
p <- p +  geom_line(aes(x=Date,y=pcs),data=red.monthly,color="red")
p
```

For red take monthly data untill end of 2019 and continue with daily data from there.


```{r}
plat.2004 <- monthly2004[,c("month","year","Trombosyyttivalmisteet")]
colnames(plat.2004) <- colnames(plat.monthly)
plat.2004$`month(date)` <- as.integer(plat.2004$`month(date)`)
plat.2004$`year(date)` <- as.integer(as.character(plat.2004$`year(date)`))
plat.2004<- plat.2004[order(plat.2004$`year(date)`,plat.2004$`month(date)`),]
plat.2004$Date<- as.Date(as.yearmon(paste0(plat.2004$`year(date)`,'-',plat.2004$`month(date)`)))
head(plat.2004)
```

```{r}
plat.monthly$Date<- as.Date(as.yearmon(paste0(plat.monthly$`year(date)`,'-',plat.monthly$`month(date)`)))
p <- ggplot(plat.2004)
p <- p +  geom_line(aes(x=Date,y=pcs))
p <- p +  geom_line(aes(x=Date,y=pcs),data=plat.monthly,color="red")
p
```

All looks good.

# Glue data together

```{r}
min(red.2004$Date)
max(red.2004$Date)
min(red.monthly$Date)
max(red.monthly$Date)
```
```{r}

red.monthly <- rbind(red.2004[red.2004$Date < as.Date("2019-01-01") ,],red.monthly[red.monthly$Date >= as.Date("2019-01-01") & red.monthly$Date < as.Date("2020-07-01")  ,])
p <- ggplot(red.monthly)
p <- p +  geom_line(aes(x=Date,y=pcs))
p
```


```{r}
# Dates
#months <- seq(from = as.Date("2009-01-01"), to = max(distr$date), by = "month")
months <- seq(from = min(red.monthly$Date), to = max(red.monthly$Date), by = "month") #This needs to be tuned based on your data set

# Adjustment series
adj <- as.numeric(bizdays(ts(months, start = decimal_date(as.Date("2009-01-01")), frequency = 12), FinCenter = "Zurich"))
# scaler <- as.numeric(bizdays(ts(1, start = decimal_date(months[length(months)]), frequency = 12), FinCenter = "Zurich")) This was written to scale a singular forecasted month back to real values, for saving-to-file purposes

reverse_adj <- as.numeric(bizdays(ts(seq(23), start = decimal_date(months[length(months)]), frequency = 12), FinCenter = "Zurich")) # This is the old implementation that used to be fed into the forecasting function. We'll now repurpose it so it can be used both for tabling and plotting.

# Create a master frame
monthly <- data.frame(date = months,
                      red = red.monthly$pcs/adj
                      #plat = plat.monthly$pcs/adj #First I need to figure out how to glue the data together
                      )

monthly_real <- data.frame(date = months,
                           red = red.monthly$pcs
                           #plat = plat.monthly$pcs #First I need to figure out how to glue the data together
                           )

beginning <- head(tail(monthly$date, ((rw_years+1) * 12 + 1)), 1) ## Define beginning of (monthly) time here THIS IS FOR USING ONLY LAST (rw_years +1) YEARS OF DATA for chosing model

last_month <- tail(monthly$date, 1) # Not using "today()" as the data may not reach to current date

# We will need these stored
modelnames <- c("SNAIVE", "5-MA", "7-MA", "9-MA", "12-MA", "STL", "ETS", "TBATS", "STLF", "ARIMAX", "DYNREG", "NN", "COMBINED")

file <- "fulldata.rdata"
out <- list(monthly=monthly, monthly_real=monthly_real)
save(out,file=file)
beginning
min(monthly$date)
max(monthly$date)

```



### All red
```{r monthly_model_selection_red}
# Define the series to be used
# We want to use 4 years of data. 3 years for the width of the rolling window and we'll let that run for a year.
#segment <- head(tail(monthly$red, ((rw_years+1) * 12 + 1)), ((rw_years+1) * 12))
#series.ts <- ts(segment, start = decimal_date(beginning), frequency = 12)
#Instead use full data
series.ts <- ts(monthly$red,start =  c(2004, 1), frequency = 12)

rw_ys <- c(3:8)
for(i in rw_ys) {
  b <- beginning <- head(tail(monthly$date, ((rw_years+1) * 12 + 1)), 1)
  cat("beginning:",as.Date(b),"rw_years:",i,"\n")
  cat("Red\n", file=paste0("rw_testing/m_errors_rwy", i, "_mean.txt"), append=TRUE)
  cat("Red\n", file=paste0("rw_testing/m_errors_rwy", i, "_all.txt"), append=TRUE)
  chosen.model <- select_model(b, series.ts, "monthly", i)
  modelname <- modelnames[chosen.model]
  cat(str_replace_all(paste0("Red;", modelname, "\n")," ",""), file=paste0("rw_testing/m_errors_rwy", i, "_chosen.txt"), append=TRUE)
  cat("\n", file=paste0("rw_testing/m_errors_rwy", i, "_mean.txt"), append=TRUE)
  cat("\n", file=paste0("rw_testing/m_errors_rwy", i, "_all.txt"), append=TRUE)
}
```

N.B. length of "rw_testing/m_errors_rwy", i, "_mean.txt" will be one month less than the actual data.


### Platelets
```{r monthly_model_selection_plat}
# Define the series to be used
series.ts <- ts(monthly$red,start =  c(2004, 1), frequency = 12)

rw_ys <- c(3:8)
for(i in rw_ys) {
  b <- beginning <- head(tail(monthly$date, ((rw_years+1) * 12 + 1)), 1)
  cat("beginning:",as.Date(b),"rw_years:",i,"\n")
  cat("Plat\n", file=paste0("rw_testing/m_errors_rwy", i, "_mean.txt"), append=TRUE)
  cat("Plat\n", file=paste0("rw_testing/m_errors_rwy", i, "_all.txt"), append=TRUE)
  chosen.model <- select_model(b, series.ts, "monthly", i)
  modelname <- modelnames[chosen.model]
  cat(str_replace_all(paste0("Plat;", modelname, "\n")," ",""), file=paste0("rw_testing/m_errors_rwy", i, "_chosen.txt"), append=TRUE)
  cat("\n", file=paste0("rw_testing/m_errors_rwy", i, "_mean.txt"), append=TRUE)
  cat("\n", file=paste0("rw_testing/m_errors_rwy", i, "_all.txt"), append=TRUE)
  
}
```


```{r}
ts.red <- ts(monthly$red, frequency = 12)
decomposed <- stl(ts.red,s.window = "periodic")
autoplot(decomposed)
filename <- filename <- paste0(ROOTDIR, "/rw_testing/img/all_years/red_decomposition_gg_FIN.pdf")
ggsave(filename=filename, width = 180,  height = 180,units="mm", dpi=600, scale=1.0)
```

```{r}
seasonal <- decomposed$time.series[,1]
ggAcf(seasonal)
```

```{r}

plot.seasonal <- as.data.frame(cbind(seasonal[1:12],1:12))
colnames(plot.seasonal) <- c("seasonal","month")
p  <- ggplot(plot.seasonal)
p <- p + geom_line(aes(y=seasonal,x=month)) + scale_x_continuous(breaks=1:12,labels=c("Jan","Feb","Mar","Apr","May","Jun","Jul","Aug","Sep","Oct","Nov","Dec")) + xlab("Month") + ylab("Seasonal (pcs)")
#c("Jan","Feb","Mar","Apr","May","Jun","Jul","Aug","Sep","Oct","Nov","Dec")
p
filename <- filename <- paste0(ROOTDIR, "/rw_testing/img/all_years/red_decomposition_seasonal_gg_FIN.pdf")
ggsave(filename=filename, p, width = 180,  height = 180,units="mm", dpi=600, scale=1.0)
```


